---
title: "Standard Errors LA County Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Standard Errors LA County Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, we'll load the `maar` package. You may install by uncommenting the `remote::install_github command` if you wish.
```{r setup}
#remotes::install_github('shamindras/maar')
library(maar)
```

We try to replicate the results of table 1 in ... 

Let's load the data and briefly examine it.
```{r, load_data}
df <- vroom::vroom('http://www-stat.wharton.upenn.edu/~buja/STAT-961/Homeless_LA_by_Census_Tracts.csv')
DT::datatable(data = head(df))
```

## Fitting the OLS model

We now fit an linear model of the number of homeless people (`StreetTotal`) on the other features via OLS.
```{r}
mod_fit <- lm(StreetTotal ~ ., df)
```

## Computing standard errors 

Let's first obtain the coefficient's standard errors returned from the `lm` object.
```{r}
se_lm <- broom::tidy(mod_fit) %>% dplyr::select(term, std.error)
```


We now compute the standard errors via $10^3$ bootstrap replications of the dataset of the same size as the original dataset.
```{r}
se_emp <- maar::empirical_bootstrap(mod_fit = mod_fit, B = 1000) %>%
  tidyr::unnest(boot_out) %>%
  dplyr::group_by(term) %>%
  dplyr::summarise(std.error.boot = sd(estimate))
```

Then we obtain the standard errors using the White sandwich estimator.
```{r}
se_sand <- diag(maar::comp_sandwich_qr_var(mod_fit)) %>% sqrt()
```

## Comparing standard errors

We combine the standard errors into one tibble.
```{r}
se_comb <- broom::tidy(mod_fit) %>%
  dplyr::select(term, estimate) %>%
  tibble::add_column(std.error.lm = dplyr::pull(se_lm, std.error)) %>%
  tibble::add_column(std.error.boot = dplyr::pull(se_emp, std.error.boot)) %>%
  tibble::add_column(std.error.sand = se_sand)
# se_comb %>% knitr::kable(x=.)
se_comb %>%
  DT::datatable(data = .) %>%
  DT::formatRound(
    table = ., columns = c("term", "estimate", "std.error.lm", "std.error.boot", "std.error.sand"),
    # valueColumns = c('Term', 'Estimate', '$SE_{lin}$', '$SE_{boot}$', '$SE_{sand}$'),
    digits = 3
  )
```

We can also compute the ratios of the standard errors and the t-statistics as in the paper.
```{r}
t_stats <- se_comb %>%
  dplyr::mutate(
    rat.boot.vs.lm = std.error.boot / std.error.lm,
    rat.sand.vs.lm = std.error.sand / std.error.lm,
    rat.sand.vs.boot = std.error.sand / std.error.boot,
    t.lm = estimate / std.error.lm,
    t.boot = estimate / std.error.boot,
    t.sand = estimate / std.error.sand
  )
t_stats %>% DT::datatable(data = .) %>%
  DT::formatRound(table = .,  columns =c("term", "estimate", "std.error.lm", "std.error.boot", "std.error.sand", "rat.boot.vs.lm", "rat.sand.vs.lm", "rat.sand.vs.boot", "t.lm", "t.boot", "t.sand"), digits = 3)
```



