---
# see https://www.jstatsoft.org/pages/view/style#what-are-the-capitalization-rules-in-jss-what-is-title-style-and-sentence-style
documentclass: jss
author:
  - name: Riccardo Fogliato # (!!!!) order of authors to be revisited (!!!!)
    affiliation: 'Carnegie Mellon University'
  #  affiliation: | doesn't fit
  #    | Department of Statistics and Data Science
  #    | Carnegie Mellon University
    address: |
      | FMS 317, 5000 Forbes Ave
      | Pittsburgh, PA 15213, United States
    email: \email{rfogliat@andrew.cmu.edu}
  - name: Shamindra Shrotriya
    affiliation: 'Carnegie Mellon University'
    address: |
      | FMS 317, 5000 Forbes Ave
      | Pittsburgh, PA 15213, United States
    email: \email{sshrotri@andrew.cmu.edu}
  - name: Arun Kuchibotla
    affiliation: 'Carnegie Mellon University'
    address: |
      | Baker Hall, 4909 Frew St
      | Pittsburgh, PA 15213, United States
    email: \email{arunku@stat.cmu.edu}
    # use a different affiliation in adress field (differently formated here)
    #affiliation2: Universitat Autònoma de Barcelona
title:
  formatted: "\\pkg{maars:} Tidy Inference Under the `Models as Approximations' Framework in \\pkg{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "maars: Tidy Inference Under the `Models as Approximations' Framework in R"
  # For running headers, if needed
  short:     "\\pkg{maars}: Models as Approximations"
abstract: >
  Linear regression using ordinary least squares (OLS) 
  is a critical part of a statistician's
  toolkit. In \pkg{R}, this is elegantly implemented 
  via the \code{lm()} and related functions. However, this functionality is based on the 
  unrealistic assumption that the linear model is well-specified. A large 
  body of econometric and statistical research has focused on performing OLS inference under 
  more practical assumptions. There is a need for a comprehensive workflow in $\pkg{R}$
  for OLS under these practical assumptions. In this paper, we introduce our \pkg{R} package \pkg{maars}, 
  to enable a \textit{tidy} inferential workflow in the misspecified OLS setting. Under potential 
  misspecification, we demonstrate how the \pkg{maars} package performs variance estimation, 
  confidence interval computation, hypothesis testing, and diagnostics. The outputs of \pkg{maars} 
  functions are tailored for further exploration using the \pkg{tidyverse} \pkg{R} packages.
keywords:
  # at least one keyword must be supplied
  formatted: [Ordinary Least Squares (OLS), Sandwich variance, Bootstrap, Model Misspecification, "\\pkg{tidyverse}"]
  plain:     [ordinary least squares (OLS), sandwich variance, bootstrap, model misspecification, tidyverse]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
    includes:
      in_header: ["Latex/macros_01_proof_envs.sty", "Latex/macros_02_operators_commands.sty", "Latex/macros_03_symbols.sty", "Latex/macros_04_propernames.sty", "Latex/macros_05_reviewer.sty"]
bibliography: references.bib 
---



```{r, setup, include=FALSE, purl=FALSE}
options(prompt = 'R> ', continue = '+ ')
knitr::opts_chunk$set(purl = TRUE)
```

```{r, child=here::here('paper', '00-introduction.Rmd'), purl=TRUE}
```

# Introduction

This template demonstrates some of the basic LaTeX that you need to know to
create a JSS article.

## Code formatting

In general, don't use Markdown, but use the more precise LaTeX commands instead:

* \proglang{Java}
* \pkg{plyr}

One exception is inline code, which can be written inside a pair of backticks
(i.e., using the Markdown syntax).

If you want to use LaTeX commands in headers, you need to provide a
`short-title` attribute. You can also provide a custom identifier if necessary.
See the header of Section \ref{r-code} for example.

# \proglang{R} code {short-title="R code" #r-code}

Can be inserted in regular R markdown block.

```{r}
x <- 1:10
x
```

## Features specific to \pkg{rticles} {short-title="Features specific to rticles"}

* Adding short titles to section headers is a feature specific to \pkg{rticles}
(implemented via a Pandoc Lua filter). This feature is currently not supported
by Pandoc and we will update this template if 
[it is officially supported in the future](https://github.com/jgm/pandoc/issues/4409).
* Using the `\AND` syntax in the `author` field to add authors on a new line.
This is a specific to the `rticles::jss_article` format.

# References

<div id="refs"></div>

```{r, child=here::here('paper', '99-sessioninfo.Rmd'), purl=TRUE}
```
